---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# LawEdwards2015

This package contains eyetracking data from the mispronunciation experiment
reported in [Law and Edwards (2015)](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC4618685/).

The purpose of this package is to provide pre-packaged eyetracking data from a
well-documented experiment to support testing and development of code and
statistical models about eyetracking data. This package is *not* an open-data or
reproducible-research supplement for that publication.

## Installation

You can install LawEdwards2015 from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("tjmahr/LawEdwards2015")
```

## Example

This package contains frame-by-frame looking data:

```{r example}
library(LawEdwards2015)
library(dplyr, warn.conflicts = FALSE)

law_edwards_2015
```

Use `AggregateLooks()` from the [lookr package](https://github.com/tjmahr/lookr) to get looking proportions collapsed across trials.

```{r}
aggregated <- law_edwards_2015 %>% 
  filter(between(Time, -500, 2000)) %>% 
  # First two trials were familarization
  filter(Condition != "FAM") %>% 
  lookr::AggregateLooks(Subject + Condition + Time ~ GazeByImageAOI) %>% 
  tibble::as_data_frame()
aggregated
```

Make a nice plot of the raw data. 

```{r cond-over-time}
library(ggplot2)
theme_aligned <- theme(
  axis.title.x = element_text(hjust = .995), 
  axis.title.y = element_text(hjust = .995))

condition_labels <- c(
  "real" = "real word",
  "MP" = "mispronunication",
  "nonsense" = "nonword"
)

aggregated$heard <- aggregated$Condition %>% 
  factor(levels = names(condition_labels), labels = condition_labels)
  
ggplot(aggregated) + 
  aes(x = Time, y = Proportion, color = heard) + 
  geom_hline(yintercept = .5, size = 2, color = "white") +
  stat_summary(fun.data = mean_se, geom = "pointrange") + 
  labs(x = "Time relative to target noun onset (ms)", 
       y = "Proportion of looks to familiar image",
       color = "Child hears",
       caption = "Mean ± SE") + 
  theme_grey(base_size = 12) + 
  theme_aligned + 
  theme(legend.position = "top",
        legend.justification = "left") 
```

Compare to [Figure
2](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC4618685/figure/F2/) of the
article. (The data for that plot used was pre-processed to remove trials with
excessive missing and to downsample looks into 50 ms bins, whereas this plot 
uses raw data).
