---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# LawEdwards2015

This package contains eyetracking data from the mispronunciation experiment
reported in [Law and Edwards (2015)](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC4618685/).

The purpose of this package is to provide pre-packaged eyetracking data from a
well-documented experiment to support testing and development of code and
statistical models about eyetracking data. This package is *not* an open-data or
reproducible-research supplement for that publication.

## Installation

You can install LawEdwards2015 from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("tjmahr/LawEdwards2015")
```

## Example

This package contains frame-by-frame looking data:

```{r example}
library(LawEdwards2015)
library(dplyr, warn.conflicts = FALSE)

law_edwards_2015
```
